\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red}


\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Yaguang (Ozzy)}{Tao}
\address{3/9 Toward St, Murrumbeena, VIC 3163}
\mobile{0434808020}
\github{Ozzytao}
\email{taoyaguang@gmail.com}
\linkedin{yaguang-tao-7a207970}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}
%\linkedin{linkedin name}
%\reddit{reddit account}
%\xing{xing name}
%\extrainfo{test} % Other text you want to include on this line

\position{Data Scientist}
\quote{``everything is related to everything else, but near things are more related than distant things."} % A quote or statement

\begin{document}
\makecvheader % Print the header

\lettersection{Qualifications}
\begin{enumerate}
\item PhD in Mathematics, Computer Science, Electrical and Electronic Engineering or a relevant field.
I'm a PhD candidate in Geospatial Science expected to submit in a month. My PhD research is about movement modeling which concerns about representing and analysing movement data observed by fixed sensors.

\end{enumerate}

\lettersection{Experience, Knowledge and Skills}
\begin{enumerate}
    \item Experience working with and analysing real-world data, especially time series and general spatio-temporal data sets generated by physical sensors.
    
    My PhD project involves analysing various types of movement data, including GPS trajectory data and transit card records, which are all real-world spatio-temporal data sets. These data sets are of different spatio-temporal granularity. By carefully modeling these data, I was able to do similar analytic tasks on these data sets and extract useful spatio-temporal patterns.  
    
    \item Sound Knowledge of at least three areas out of applied mathematics, artificial intelligence, computational intelligence, data analytics, machine learning, signal and image processing, and Internet of Things.
    
    
    
    \item A strong record of high quality peer reviewed publications in highly ranked international journals and/or conferences relative to opportunity.
    \item Demonstrated ability to conduct research in competitive and/or industry projects.
    \item Demonstrated ability to support the development of research grant applications, especially ARC Linkage applications
    \item Ability to conduct high-quality research individually and collaboratively as a member of a research team
    \item Capacity to undertake and contribute to industry focused research
    \item Experience in contributing to the supervision of undergraduate honours and/or research higher degree students
    \item Demonstrated excellent oral, written communication and presentation skills
    \item Demonstrated organisational skills including the ability to demonstrate scientific rigour and maintain a high stand of laboratory and data record keeping.
\end{enumerate}

\lettersection{Personal Qualities}
\begin{enumerate}
    \item Interpersonal skills that support the ability to establish and maintain highly effective working relationships with a diverse range of people including students, the staff of the Faculty and School and with other members of the University
    \item Ability to adapt the changes in the environment and effectively meet new challenges
    \item Commitment to the University's Mission, Core Commitments and Values which include - excellence, academic freedom, collegiality, continuous improvement, ethical behaviour, accountability and environmental responsivility.
\end{enumerate}

\end{document}