%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------
\begin{cventries}
\cventry
{Java programmer Intern}
{Leighton O’Brien Pty Ltd}
{Melbourne, Australia}
{Mar. 2016 - Jun. 2016}
{
\begin{cvitems}
\item{Design mapping functionalities for location-based data.}
\item{Add GPS support for current system;}
\item{Design and implement task scheduling module with location
considered;}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Research Assistant}
{The University of Melbourne}
{Melbourne, Australia}
{Dec. 2014 - Jul. 2015}
{
\begin{cvitems}
\item{GIS tools development: Design and develop plugins and
tools for research needs. Specifically, Python frameworks
PyQt and PyQGIS are used for developing interactive map
legend for QGIS}
\item{Data visualization research: Exploring ways for embedding
information into map layout which is natural for user to
interpret}
\item{Algorithm Testing: Design experiments for verifying given sensor network algorithms and testing under Python/Scipy environment}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Web Developer Intern} % Job title
{Thinkspatial Pty Ltd} % Organization
{Melbourne, Australia} % Location
{Jul. 2014 - Oct. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designing, developing and deploying a web mapping
application}
\item {Data analytics for GIS data}
\end{cvitems}
}

%------------------------------------------------    



%------------------------------------------------

\end{cventries}